---
title: "My R Markdown Primer"
author: "Jonathan Gonzalez"
date: "2026-04-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

R Markdown is a file format that allows users to combine narrative writing, R code, and mathematical notation in a single document. This makes it easier to organize analysis and ensures that results are reproducible.

# Narrative Section

One of the main advantages of R Markdown is that it integrates code and explanation together. Instead of writing results separately, the output is generated directly from the code, reducing errors and improving clarity.

Inline math example: $\alpha + \beta = \gamma$

Displayed equation:

$$
y = mx + b
$$

# Load Data

```{r}
library(ggplot2)
data("economics", package = "ggplot2")
head(economics)
```



# Summary Statistics
```{r}
#The following output shows summary statistics for unemployment:

summary(economics$unemploy)
```


# Visualization
```{r}
ggplot(economics, aes(x = date, y = unemploy)) +
  geom_line(color = "blue") +
  labs(
    title = "Unemployment Over Time",
    x = "Date",
    y = "Number Unemployed"
  )
```




